D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem

### 2024-02-14 ootavacuous.tex
OOTA: Add roadmap
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

>>>>

Section~\ref{sec:OOTA: rf vs. rfe}
demonstrates advantages of formulating an OOTA cycle as a cycle in
sdep $\cup$ rfe instead of the traditional sdep $\cup$ rf.
Section~\ref{sec:Properties of Semantic Dependencies}
then discusses properties of semantic dependences, showing that they
are functions of executions rather than strictly of source code.
